\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Assignment 01: Title\\
{\footnotesize \textsuperscript{}CSE-0318 Summer 2021 }
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{jannatul arefin}
\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
\textit{State University of Bangladesh (SUB)}\\
Dhaka, Bangladesh \\
arefinprima@gmail.com} 
%\and
%\IEEEauthorblockN{Khan Md. Hasib}
%\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
%\textit{State University of Bangladesh (SUB)}\\
%Dhaka, Bangladesh  \\
%hasib@sub.edu.bd}
}

\maketitle

\begin{abstract}

PC programming has been progressively utilized in different fields. Computer programming plan strategies has been utilized in this paper, Sports Management System has been pre-planned based on use of computer programming hypothesis and technique, under this reason, the real administration of sports and framework programming have been created. The plan of information stream chart was clear and sensible, which has assumed a significant part in programming improvement. It has been demonstrated that the games the board framework has been wonderful made with proficiency configuration, quick handling related issues utilizing programming techniques. In this day and age, programming improvement can be intricate and profoundly serious. A few components add to the intricacy, especially if the product has an electronic UI and is a conveyed application. 



\end{abstract}n


\begin{IEEEkeywords}
The word mostly used in your report.
HTML, CSS, JavaScript,Laravel,Adobe Photoshop
\end{IEEEkeywords}

\section{Introduction}
BDSports is a web application for enjoy the sports entertainment. User can enjoy any type of international sports in this application. The sports lover people take the entertainment and refresh their mind through the sports. User can easily buy their desirable product from this application.

Definition and objective of your assignment or report.

\section{Literature Review}

Any work that previous any developer or researcher did, mention them in a few words.


\section{Proposed Methodology}

The methodology you work, explain here with code and other items.


\subsection{Equations}


\section{Conclusion and Future Work}

In future, what you bring in your project and the idea of your work.

\section*{Acknowledgment}

I would like to thank my honourable\textbf{Khan Md. Hasib Sir} for his time, generosity and critical insights into this project.




\vspace{12pt}

\end{document}
